---
title: "Pilot study APEROL: questionnaire data"
author: "Mandy Klatt, Gregor Kachel and Anne Deiglmayr"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### HOW TO PREPARE DATA IN EXCEL ###
# use filter to select only lines with an ID in it 
# (i.e. exclude all empty lines or lines with na, ?, x, etc)
# select all columns except the columns for comments
# copy/paste into a new spreadsheet
# click "save as" and choose file type "tab-delimited-text"
####################################

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/short_questionnaire_data_2001211.txt",sep="\t", header=T) 


# loading packages
# install.packages("stringr") # install stringr to use the filter() function with text data
library(stringr)

# if a package is not installed on the current machine, it will install it
if (!require(tidyverse)) install.packages('tidyverse'); library(tidyverse)

# suppress "summarize" info. 
# if this line is committed, each table using the summarize function will be accompanied with a warning from the console
options(dplyr.summarise.inform = FALSE)

### checking for missing values
apply(is.na(raw.data), 2, which)

# knock out NAs
raw.data <- raw.data  %>% filter(
  personID != "NA")


# view (raw.data)
# str(raw.data)

```

# Short Summary
This report provides a summary of the questionnaire data of the first pilot APEROL. The aim was to explore connections between the visual attention of the teacher and students’ in-class experience of the teachers’ "withitness". The study was conducted as a lab study with simulated scripted mini-lessons (10min per lesson). Data was collected from N = 8 teachers and N = 1 observer in 2 sessions. 

In each session, one subject took the role of teacher, while the other teachers acted as the class. After each lesson, the subjects answered items on classroom management, especially on the teacher's behaviour, using validated questionnaires. An external observer also answered a questionnaire. In addition, the teacher was asked to give a self-assessment on his/her classroom management. 


### Data collection
For the pilot study, we collected questionnaire data from N = 8 subjects in `r sum(n_distinct(raw.data$session))` sessions. The questionnaires were answered after each lesson (10min) by an observer, the teacher and the three teachers acting as the class. 


The table shows the state of data collection as of `r Sys.Date()`.

```{r overview demographics data table, echo=FALSE}

# counting male / female 
sex <- raw.data %>% filter(what == "head")

# # converting column "group" from character into numeric 
# raw.data <- raw.data %>%  mutate(group = as.numeric(as.character(group)))

# demographics, grouped by group, filtered by perspective (N, meanage, max, min age)
raw.data %>% # select data
  filter(perspective == "teacher") %>%
  group_by(group) %>%
  summarise(N = n_distinct(groupID),
            "male" = sum(sex),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age)
            ) %>% 
  knitr::kable(digits = 2)

```



### Plotting scales

The graphs provide line plots for each perspective and target, plotted for the following scales for both sessions:

(1) classroom management
(2) positive climate and motivation
(3) clarity and structuredness
(4) activation and support
(5) presence: posture and gaze
(6) presence: voice
(7) presence: verbal and non-verbal intervention
(8) turn taking
(9) natural behaviour


#### Session 1 

#### classroom management

```{r mean classroom management by session, echo = FALSE}

### classroom management session 1 

# filter by parameter variable, i.e. create a subset for each session
km1.data <- raw.data %>% filter(scale == "Klassenmanagement",
                               session == "1")

view (km1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
km1.data <- km1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***classroom management*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

``` {r classroom management data table, echo=FALSE}

km1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```

```{r classroom management line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
km1.plot.sd <- km1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
km1.plot<-ggplot(data = km1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = km1.data, y = "value", x = NULL,
       title="classroom management" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
km1.plot

```


#### positive climate and motivation

```{r mean positive climate and motivation by session, echo = FALSE}

### positive climate and motivation session 1 

# filter by parameter variable, i.e. create a subset for each session
lkm1.data <- raw.data %>% filter(scale == "Lernförderliches Klima und Motivierung",
                               session == "1")

view (lkm1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
lkm1.data <- lkm1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***positive climate and motivation*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r positive climate and motivation data table, echo=FALSE}

lkm1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r positive climate and motivation line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
lkm1.plot.sd <- lkm1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
lkm1.plot<-ggplot(data = lkm1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = lkm1.data, y = "value", x = NULL,
       title="positive climate and motivation" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
lkm1.plot
```

XXX Order lieber Boxplots? Da würde ich gern noch die Mittelwerte mit einer Linie verbinden. XXX

```{r plot boxplot by groups, echo = FALSE}
lkm1.boxplot <- ggplot() +
              geom_boxplot(data = lkm1.plot.sd, 
                           aes(x = perspective, y = mean), )+ 
  geom_line(data = lkm1.plot.sd, mapping = aes(x = perspective, y = mean)) + 
  geom_jitter(data = lkm1.plot.sd, aes(x = perspective, y = mean, colour = target), size = 2, width = 0.1) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 5), limits = c(0,4))+
  labs(x="perspective", y="value", title = "positive climate and motivation")+ 
  theme_classic()
lkm1.boxplot

```

#### clarity and structuredness

```{r mean clarity and structuredness by session, echo = FALSE}

### clarity and structuredness session 1 

# filter by parameter variable, i.e. create a subset for each session
ks1.data <- raw.data %>% filter(scale == "Klarheit und Strukturiertheit",
                               session == "1")

view (ks1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
ks1.data <- ks1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***clarity and structuredness*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r clarity and structuredness data table, echo=FALSE}

ks1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r clarity and structuredness line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
ks1.plot.sd <- ks1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
ks1.plot<-ggplot(data = ks1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = ks1.data, y = "value", x = NULL,
       title="clarity and structuredness" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
ks1.plot
```


#### activation and support

```{r mean activation and support by session, echo = FALSE}

### activation and support session 1 

# filter by parameter variable, i.e. create a subset for each session
af1.data <- raw.data %>% filter(scale == "Aktivierung und Förderung",
                               session == "1")

view (af1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
af1.data <- af1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***activation and support*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r activation and support data table, echo=FALSE}

af1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r activation and support line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
af1.plot.sd <- af1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
af1.plot<-ggplot(data = af1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = af1.data, y = "value", x = NULL,
       title="activation and support" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
af1.plot
```


#### presence: posture and gaze

```{r mean presence: posture and gaze by session, echo = FALSE}

### presence: posture and gaze session 1 

# filter by parameter variable, i.e. create a subset for each session
phb1.data <- raw.data %>% filter(scale == "Präsenz/Haltung_Blick",
                               session == "1")

view (phb1.data)

# value sometimes contained text before filtering, we have to convert the numbers to numeric
phb1.data <- phb1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: posture and gaze*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r presence: posture and gaze data table, echo=FALSE}

phb1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r presence: posture and gaze line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
phb1.plot.sd <- phb1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
phb1.plot<-ggplot(data = phb1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = phb1.data, y = "value", x = NULL,
       title="presence: posture and gaze" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
phb1.plot

```


#### presence: voice
XXX aus unerklärlichen Gründen wird mir "No data available in table" angezeigt, wenn ich versuche, Präsenz/Stimme für Session1 zu filtern. Hab den Fehler leider noch nicht gefunden... XXX
```{r mean presence: voice by session, echo = FALSE}

### presence: voice session 1 

# filter by parameter variable, i.e. create a subset for each session
ps1.data <- raw.data %>% filter(scale == "Präsenz/Stimme",
                                session == "1")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
ps1.data <- ps1.data %>%  mutate(value = as.numeric(as.character(factor(value))))

# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: voice*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX



``` {r presence: voice data table, echo=FALSE}
# 
# ps1.data %>% # select data
#   group_by(target,perspective) %>%
#   summarise(N = n_distinct(personID),
#             "mean" = round(mean(value), 2),
#             "min" = min(value),
#             "max" = max(value),
#             "sd" = sd(value),
#             "median" = median(value)
#             ) %>% 
#   knitr::kable(digits = 2)

```

```{r presence: voice line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# # to create error bars, we need to summarize the data in a separate data frame
# ps1.plot.sd <- ps1.data %>%
#   group_by(perspective, target, .drop=TRUE) %>%
#   summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )
# 
# # and here comes the long plot
# ps1.plot<-ggplot(data = ps1.plot.sd,
#                    aes(x = perspective, y = mean,
#                        group = target, colour = target)) +
#   geom_line()+
#   geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
#   theme_light() +
#   ylim(1,4)+
#   labs(data = ps1.data, y = "value", x = NULL,
#        title="presence: voice" ,
#        subtitle=NULL)+
#   theme(legend.position="bottom",
#         panel.spacing.x = ,
#         plot.title = element_text(hjust = 0.5))+
#   scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
#   coord_flip()
# ps1.plot

```




#### presence: verbal and non-verbal intervention

```{r mean presence: verbal and non-verbal intervention by session, echo = FALSE}

### presence: verbal and non-verbal intervention session 1 

# filter by parameter variable, i.e. create a subset for each session
pi1.data <- raw.data %>% filter(scale == "Präsenz/verbale_nonberbale Intervention",
                               session == "1")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
pi1.data <- pi1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***presence: verbal and non-verbal intervention*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r presence: verbal and non-verbal intervention data table, echo=FALSE}

pi1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r presence: verbal and non-verbal intervention line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
pi1.plot.sd <- pi1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
pi1.plot<-ggplot(data = pi1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = pi1.data, y = "value", x = NULL,
       title="presence: verbal and non-verbal intervention" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
pi1.plot

```

#### turn taking

```{r mean turn taking by session, echo = FALSE}

### turn taking session 1 

# filter by parameter variable, i.e. create a subset for each session
redeanteil1.data <- raw.data %>% filter(scale == "Redeanteil",
                               session == "1")

# value sometimes contained text before filtering, we have to convert the numbers to numeric
redeanteil1.data <- redeanteil1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***turn taking*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r turn taking data table, echo=FALSE}

redeanteil1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r turn taking line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
redeanteil1.plot.sd <- redeanteil1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
redeanteil1.plot<-ggplot(data = redeanteil1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1, 100)+
  labs(data = redeanteil1.data, y = "value", x = NULL,
       title="turn taking" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
redeanteil1.plot

```


#### natural behaviour

```{r mean natural behaviour by session, echo = FALSE}

### natural behaviour session 1 

# filter by parameter variable, i.e. create a subset for each session
m1.data <- raw.data %>% filter(scale == "Manipulationsitem",
                               session == "1")


# value sometimes contained text before filtering, we have to convert the numbers to numeric
m1.data <- m1.data %>%  mutate(value = as.numeric(as.character(factor(value))))


# # create  mean, min, max, sd of classroom management
# meankm1 <- mean(km1.data$value)
# minkm1 <- min(km1.data$value)
# maxkm1 <- max(km1.data$value)
# sdkm1 <- sd(km1.data$value)
# Nkm1 <- km1.data %>% summarise(N = n_distinct(personID))
# mdkm1 <- median(km1.data$value)

```

The table below shows the mean, minimum and maximum value, the standard deviation and median for the item ***natural behaviour*** in session 1 for each perspective and target. The target always corresponds with the perspective of the teacher, i.e. teacher = target A. 

XXX Die Tabellen kann ich mir vielleicht für jede Skala sparen? XXX

``` {r natural behaviour data table, echo=FALSE}

m1.data %>% # select data
  group_by(target,perspective) %>%
  summarise(N = n_distinct(personID),
            "mean" = round(mean(value), 2),
            "min" = min(value),
            "max" = max(value),
            "sd" = sd(value),
            "median" = median(value)
            ) %>% 
  knitr::kable(digits = 2)

```


```{r natural behaviour line plots,  fig.height = 4, message = FALSE, warning = FALSE , echo=FALSE}

# to create error bars, we need to summarize the data in a separate data frame
m1.plot.sd <- m1.data %>%
  group_by(perspective, target, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
m1.plot<-ggplot(data = m1.plot.sd,
                   aes(x = perspective, y = mean,
                       group = target, colour = target)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  labs(data = m1.data, y = "value", x = NULL,
       title="natural behaviour" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
m1.plot
```


### TO DO 

- session 2 plotten
- anderen plot für redeanteil (barplot?)
- fehler finden für presence: voice


# References

R Core Team (2019). R: A language and environment for statistical computing. R Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686, https://doi.org/10.21105/joss.01686


